---
title: "FightML_HitsLandedByArse"
author: "Janis Corona"
date: "10/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This machine learning program examines the Arse May 2019 UFC fight

<https://www.espn.com/mma/fightcenter/_/id/401107798/league/ufc> has access to the 3 rounds of 5 minutes fight 5/18/2019 The csv file is found at: <https://github.com/JanJanJan2018/FightML/blob/master/ArseErosaFightAudit.csv> 

Predict the number of hits Arse lands based on the seconds into the round, elapsed since last action, cumulative number of hits received/landed/missed and number of hits received total for that round This data is split into a training set of 70% and a testing set of 30% based only on those instances action other than circling/standing/stepping away/toward/to the side occurs There are 224 instances of 156 training set samples of each second of action, and the remaining 68 are testing samples of each second of action


```{r}
ArseErosa <- read.csv('ArseErosaFightAudit.csv', 
                       sep=',', header=TRUE, 
                       na.strings=c('','NA'))#224X18
ArseErosa <- ArseErosa[,1:8]
```

```{r}
ArseErosa
```

```{r}
head(ArseErosa)
```

```{r ,warning=FALSE,error=FALSE,message=FALSE}
library(caret)
library(randomForest)
library(MASS)
library(gbm)
library(dplyr)
```

```{r cars}
set.seed(189678345)
```

```{r}
inTrain <- createDataPartition(y=ArseErosa$Hits.Lnd.A, p=0.7, list=FALSE)

trainingSet <- ArseErosa[inTrain,]
testingSet <- ArseErosa[-inTrain,]

```

```{r, message=FALSE, error=FALSE, warning=FALSE}
system.time(rfMod <- train(Hits.Lnd.A~., method='rf', data=(trainingSet), 
               trControl=trainControl(method='cv'), number=5))

```

```{r}
plot(rfMod)
```

```{r, message=FALSE, error=FALSE, warning=FALSE}
system.time(gbmMod <- train(Hits.Lnd.A~., method='gbm', data=trainingSet, verbose=FALSE ))

```

```{r}
plot(gbmMod)
```

```{r}
predRF <- round(predict(rfMod, testingSet))
predGbm <- round(predict(gbmMod, testingSet))

predDF <- data.frame(predRF, predGbm, type=testingSet$Hits.Lnd.A)
predDF

```

```{r, warning=FALSE, error=FALSE,message=FALSE}
CombinedModels <- train(type~., method='gam', data=predDF)
CombinedPredictions <- round(predict(CombinedModels, predDF))
CombinedPredictions

```

```{r}
sum <- sum(CombinedPredictions==testingSet$Hits.Lnd.A)
length <- length(testingSet$Hits.Lnd.A)
accuracy_CP1 <- sum/length #97.01

sum <- sum(predRF==testingSet$Hits.Lnd.A)
length <- length(testingSet$Hits.Lnd.A)
accuracy_rfMod <- (sum/length) #97.01

sum <- sum(predGbm==testingSet$Hits.Lnd.A)
accuracy_Gbm <- (sum/length) #97.01

```

```{r, message=FALSE, error=FALSE, warning=FALSE}
system.time(knnMod <- train(Hits.Lnd.A  ~ .,
                method='knn', preProcess=c('center','scale'),
                tuneLength=10, trControl=trainControl(method='cv'), data=trainingSet))

```

```{r}
plot(knnMod)
```

```{r, warning=FALSE}
system.time(rpartMod <- train(Hits.Lnd.A ~ ., method='rpart', tuneLength=9, data=trainingSet))
```

```{r}
plot(rpartMod)

```

```{r, warning=FALSE}
system.time(glmMod <- train(Hits.Lnd.A ~ ., 
                method='glm', data=trainingSet))
```

```{r}
predKNN <- round(predict(knnMod, testingSet))
predRPART <- round(predict(rpartMod, testingSet))
predGLM <- round(predict(glmMod, testingSet))

df3 <- cbind(predKNN, predRPART, predGLM,testingSet$Hits.Lnd.A)
colnames(df3)[4] <- 'TrueValue'

```

```{r}
length=length(testingSet$Hits.Lnd.A)

sumKNN <- sum(predKNN==testingSet$Hits.Lnd.A)
sumRPart <- sum(predRPART==testingSet$Hits.Lnd.A)
sumGLM <- sum(predGLM==testingSet$Hits.Lnd.A)

accuracy_KNN <- sumKNN/length 
accuracy_RPART <- sumRPart/length 
accuracy_GLM <- sumGLM/length 

predDF3 <- data.frame(predRF,predGbm,df3)

```

```{r, warning=FALSE}
system.time(CombinedModels <- train(TrueValue ~ ., method='gam', data=predDF3))
```

```{r}
CombinedPredictions2 <- round(predict(CombinedModels, predDF3))
accuracy_CP2 <- sum(CombinedPredictions2==testingSet$Hits.Lnd.A)/length 

predDF4 <- data.frame(predDF3, CombinedPredictions2)
colnames(predDF4)

```

```{r}
predDF4 <- predDF4[,c(1:5,7,6)]
colnames(predDF4)

```

```{r}
results <- c(round(accuracy_rfMod,2),  
              round(accuracy_Gbm,2), 
             round(accuracy_KNN,2), round(accuracy_RPART,2),
             round(accuracy_GLM,2), 
             round(accuracy_CP2,2), round(100,2))

results <- as.factor(results)
results <- t(data.frame(results))#1X7
colnames(results) <- colnames(predDF4)
Results <- rbind(predDF4, results) #68X7
Results
#write.csv(Results,'TrueHitsLanded_ML_predictionResults.csv', row.names=FALSE)

```



